---
title: "Development Data Products_Leaflet"
author: "NT"
date: "Feb 21 2021"
output:
  pdf_document: default
  html_document: default
---
# Instructions
(From Coursera's Instruction)
Create a web page using R Markdown that features a map created with Leaflet.
Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

# Review criteria
(From Coursera's Instruction)
The rubric contains the following two questions:
- Does the web page feature a date and is this date less than two months before the date that you’re grading this assignment?
- Does the web page feature an interactive map that appears to have been created with Leaflet?

# Submission
Here is the Space Needle, PikePlace Market, Seattle Aquarium, Westlake Center and Seattle Waterfront of Seattle, WA, U.S.A
## Create a leaflet map object.
```{{r setup, include=FALSE}}
library(leaflet)
library(knitr)
library(dplyr)
```
Add the marker to the map and display the map.
```{r}
map <-leaflet() %>%
   addTiles() %>%
   addMarkers(lat=47.6205131,lng= -122.3493036,popup = "SpaceNeedle, Seattle")%>%
   addMarkers(lat=47.60621,lng= -122.33207,popup = "PikePlaceMarket, Seattle")%>%
   addMarkers(lat=47.6078027,lng= -122.3431833,popup = "Seattle Aquarium, Seattle")%>%
   addMarkers(lat=47.6119908,lng= -122.3373914,popup = "Westlake Center, Seattle")%>%
   addMarkers(lat=47.6050808,lng= -122.3408405,popup = "Seattle Waterfront, Seattle")
 map 
```


``` {r}
#For FUN: cluster and circle markers
#dcluster <- data.frame(lat=runif(50, min=47.50, max =47.70 ),
                 #lng=runif(50, min=-122.35, max = -122.25 ))    
#leaflet(dcluster) %>% addTiles() %>% addCircleMarkers()
#dcluster %>%leaflet() %>%addTiles() %>%  
#addMarkers(clusterOptions = markerClusterOptions())  
```
